Work Fragmentation in Developer Interaction Data

### 2016-07-07 paper_2.tex
Reviews 2.12, 2.13 and 2.15

\subsection{Classification of events}
Mylyn events belong to two main categories: edition and selection. The UDC data do not have this, so we inferred a classification manually. Note that we reuse the same term of selection in the following text, as it was used in Mylyn data. Strictly speaking, the word "navigation" would be better suited to the variety of events present in the UDC data, but we keep the old term for consistency.
%To select the event type, we made a thorough analysis of the different events to classify them where they better fit. In comparison with Mylyn we didn't have a classification by default but the attributes can give us a very good approximation.

@@

We acknowledge that our separation of sessions in short and long interruptions is not perfect, as it is based on the presence of at least one long interruption, and nothing more. Other factors present in the group of sessions with at least one long interruption may contribute to the observed effect (for instance, these sessions may also have more interruptions overall).

@@

%Another threat is the random selection of users to get their data. Although a posterior filter allows us to manage with only valid sessions, we understand that this kind of data selection might be irresponsible. For future work we'll have another approach and be more selective on the information we work.

>>>>

\subsection{Classification of events}
Mylyn events belong to two main categories: edition and selection. The UDC data do not have this, so in order to match the classification of Mylyn we inferred the type of every event manually. So, we do not base our classification on previous work and we are aware that a change or misinterpretation could affect the final results. However, the attributes of the events offer enough information to make an accurate inference in most of the cases.

Note that we reuse the same term of selection in the following text, as it was used in Mylyn data. Strictly speaking, the word "navigation" would be better suited to the variety of events present in the UDC data, but we keep the old term for consistency.
%To select the event type, we made a thorough analysis of the different events to classify them where they better fit. In comparison with Mylyn we didn't have a classification by default but the attributes can give us a very good approximation.

@@

%We acknowledge that our separation of sessions in short and long interruptions is not perfect, as it is based on the presence of at least one long interruption, and nothing more. Other factors present in the group of sessions with at least one long interruption may contribute to the observed effect (for instance, these sessions may also have more interruptions overall).

@@

When analyzing the recovery time after an interruption, we filter out the interruptions with less than 30 minutes of activity after it. This means we only use 5\% of the interruptions. We understand that the small sample may put at risk the validity of the results but not all the interruptions are suited for this kind of analysis, as we are looking to a particular case. Also, when we look the activities during the recovery time after an interruption according to the effect (positive or negative), we calculate the frequency of activities (per type) to define when is more frequent. We understand that there could be other interpretations or explanations for this values and the changes, but we back our conclusions with observational studies.
%Another threat is the random selection of users to get their data. Although a posterior filter allows us to manage with only valid sessions, we understand that this kind of data selection might be irresponsible. For future work we'll have another approach and be more selective on the information we work.
